---
title: "Installation issues"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Installation issues}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### How to install
```{r setup, eval=FALSE}
remotes::install_github("nelstevens/daphniaRuler")
```
This command installs the package. Issues in the installation process can occur
because the daphniaruler requires python and Anaconda (or miniconda) to be installed
on your system.  

### Solve installation issues
While installing the package or when loading it you might encounter the following
error:  
Error: package or namespace load failed for ‘daphniaruler’:  
 .onLoad failed in loadNamespace() for 'daphniaruler', details:  
  call: NULL  
  error: Unable to find conda binary. Is Anaconda installed?  

This error occurs because Anaconda (or miniconda) and/or python is not installed on your system.
This should fix it:
```{r, eval=FALSE}
install.packages("reticulate")
reticulate::use_miniconda()
```

### Other issues
If this page didn't help you in the installation process or you experience other
issues using the daphniaruler please open an issue on [Github](https://github.com/nelstevens/daphniaRuler/issues). 
Your contribution will be appreciated :)
