---
title: "measure all images in a directory"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{measure_directory}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This article explains how to measure whole directories or even several
directories containing images of daphnia. Measured directories will
receive a new subdirectory containing a csv file with all measurements
specified in the argument and optionally a copy of each image with
results plotted onto the image.

### 1. load the package

```{r setup}
library(daphniaruler)
```

There should be no error messages when loading the package. In case you
experience issues see:\
<https://nelstevens.github.io/daphniaRuler/articles/installation_issues.html>

### 2. run measure_directory

Run the function measure_directory. This function requires one argument,
which is the path to a directory containing images of daphnia or a path
to a directory containing subdirectories with images of daphnia. The
function also comes with three optional arguments:\

-   write_images
-   eye_method
-   scaling_factor

**write_images** expects a logical value. When TRUE each measured image
will be copied to a subdirectory named results. All measured traits will
be plotted onto those copies. This way one can easy check whether the
measurements seem accurate.\

**find_eye** expects a logical value. When TRUE the daphniaruler will
try to detect the eye of the daphnia in each image. If successful there
will be a measurement from the eye od the daphnia to the base of the
tail and additionally a line from the base of the tail to the tip of the
tail. This should be the most accurate way the measure body size in
daphnia.

**scaling_factor** expects a logical value. When TRUE the daphniaruler
will search for a file titled Scale.txt in each directory containing
images. A template for this file can be found at:
<https://github.com/nelstevens/The-Daphnia-ruler/blob/master/Scale.txt>.
The value specified in this file should correspond to the number of
pixels that correspond to 1 cm. For example if 98 pixels make 1 cm, NUM
should be replaced by 98. Note that if Scale.txt is missing in a
directory measure_directory will fail if scaling_factor = TRUE.

```{r echo=FALSE, fig.width=6}
measure_directory(
  "../inst/sample_images",
  write_images = TRUE,
  eye_method = TRUE,
  scaling_factor = FALSE
)
```

### What should the images look like

The images ideally only contain a single individual. if other
individuals are also present in an image only the largest individual
will be measured. For optimal results try to make images as sharp as
possible. Especially the outline of the specimen should be clearly
visible.

### Note on output images

Output images with measurements plotted over will be rescaled to
720\*480p in order to save memory. However measurement outputs with
scaling_factor = NULL will correspond to pixels in the original image.
Thus measuring the drawn lines on output images with an image analysis
tool such as imageJ will show differing results.
