---
title: "Measure single images"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Measure single images}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
This article explains how to measure single images of daphnia to produce a list
containing several measurements and plot these measurements onto the image.

### 1. Load the package
```{r setup}
library(daphniaruler)
```
There should be no error messages when loading the package. In case you experience
issues see:  
https://nelstevens.github.io/daphniaRuler/articles/installation_issues.html

### 2. run measure_image
Run the function measure_image. this function requires a single argument, which
is the path to the image. This path can be either absolute or relative.
The function also comes with three optional arguments:  

* find_eye
* plot_image
* scaling_factor

find_eye expects a logical value (either TRUE or FALSE). When TRUE the package
will try to detect the eye of a daphnia within the image. If successful the will
be measurement from the eye to the base of the tail and additionally a line from 
the base of the tail to the tip of the tail. This should be the most accurate 
way the measure body size in daphnia.  
plot_image also expects a logical value (either TRUE or FALSE). When TRUE the
function will autmatically create a plot of the image with the measurements 
overplotted. Note that this feature might only work when using rstudio.  
scaling_factor expect a numeric input. It describes how many pixels occur in one 
unit of length. for example if 100 pixels correspond to 1mm then the scaling_factor would be 100.
You can calculate the scaling factor with image analysis tools such as imageJ.
If scaling_factor is NULL all measurement outputs will correspond to pixels (no scaling performed).
Here's an example what the function produces when having all optional arguments
set to default values (I'm disabling the output of the image array due to space constraints):  
```{r echo=TRUE, fig.width=6}
out <- measure_image(
  "../inst/sample_images/example1.JPG",
  find_eye = TRUE,
  plot_image = TRUE,
  scaling_factor = NULL
  )
out[names(out) != "image"]
```


### What should the image look like
The image ideally only contains a single individual. if other individuals are also
present in the image only the largest individual will be measured. For optimal 
results try to make the image as sharp as possible. Especially the outline of
the specimen should be clearly visible.

### Note on output images
Output images with measurements overplotted will be rescaled to 720*480p in order
to save memory. However measurement outputs with scaling_factor = NULL will correspond
to pixels in the original image. Thus measuring the drawn lines on output images with an image
analysis tool such as imageJ will show differing results.
